SciPy - some descriptive title here

### 2018-04-12 scipy-1.0/paper.tex
BUG: missing end bracket

    \subsubsection*{Benchmark suite}
    The airspeed velocity (asv) library enables benchmarking Python packages over their lifetimes, and the performance of the SciPy
    code base was monitored with asv starting in February of 2015 (PR \#4501). In addition to ensuring that unit tests are passing (see above),
    confirming that performance generally remains constant or improves over the commit hash history of the project allows us to objectively
    measure that our code base is improving, to empower scientific applications.

    Consider the asv benchmark results shown in Figure~\ref{fig:asv-bench}, spanning roughly nine years of project history. These demonstrate the gradual performance
    improvements in a nearest-neighbor search through \texttt{scipy.spatial.cKDTree.query()}, and can be run using the command:

@@

        \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
        \label{fig:asv-bench}
    \end{figure

>>>>

    \subsubsection*{Benchmark suite}

    The airspeed velocity (asv) library enables benchmarking Python packages over their lifetimes, and the performance of the SciPy
    code base was monitored with asv starting in February of 2015 (PR \#4501). In addition to ensuring that unit tests are passing (see above),
    confirming that performance generally remains constant or improves over the commit hash history of the project allows us to objectively
    measure that our code base is improving, to empower scientific applications.

    Consider the asv benchmark results shown in Figure~\ref{fig:asvbench}, spanning roughly nine years of project history. These demonstrate the gradual performance
    improvements in a nearest-neighbor search through \texttt{scipy.spatial.cKDTree.query()}, and can be run using the command:

@@

    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
        \caption{Airspeed velocity benchmarks for scipy.spatial.cKDTree.query() over a roughly nine year commit history time frame. The results are based on Python 2.7 performance on the master branch of the project using numpy 1.8.2 and Cython versions 0.27.3 and 0.21.1 (for improved backward compatibility). Only the L2 (Euclidean) norm is shown here, and to improve backward compatibility and sampling of the benchmarks there was no application of toroidal topology to the KDTree (boxsize argument was ignored).}
        \label{fig:asvbench}
    \end{figure}
